Algomusicology, ???, Profit

### 2016-04-02 paper.tex
Add hyperref package for URLs.
Add a couple of bibliography items.
Fix the backslash in the G string reference.
Add Blurred Lines as a section.
Add an abstract.

% Based on the template for sigplanconf LaTeX Class by Paul C. Anagnostopoulos (paul@windfall.com)
\documentclass[preprint]{sigplanconf}

\usepackage{amsmath}

@@

\title{Algomusicology, ?, Profit}
%\subtitle{Subtitle Text, if any}

@@

\begin{abstract}
This is the text of the abstract.
\end{abstract}

@@

\keywords
keyword1, keyword2

@@

\section{Air on the \\G String}
\begin{verbatim}
(comment (take 10000 (repeat (* 1000 1000 1000 1000) \G)))

@@

\section{Anti}
\begin{verbatim}

@@

\bibliographystyle{abbrvnat}

@@

\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
P. Q. Smith, and X. Y. Jones. ...reference text...

>>>>

% Based on the template for sigplanconf LaTeX Class by Paul C. Anagnostopoulos (paul@windfall.com)
\documentclass[numbers]{sigplanconf}

\usepackage{amsmath}
\usepackage{hyperref}

@@

\title{Algomusicology, ???, Profit}
%\subtitle{Subtitle Text, if any}

@@

\begin{abstract}
    In this paper I propose a novel method for converting algomusicology into profit. While my particular example
    is slightly tongue-in-cheek, my serious point is that algorithmic composition can help us deconstruct and
    disrupt traditional notions of musical authorship.
\end{abstract}

@@

%\keywords
%keyword1, keyword2

@@

\section{Air on the {\textbackslash}G String}
\begin{verbatim}
(comment (take 10000 (repeat (* 1000 1000 1000 1000) \G)))

@@

\section{Anti}

\section{Blurred Lines}
\begin{verbatim}

@@

\bibliographystyle{plainnat}

@@

\bibitem{Overtone} Aaron, Sam and Rose, Jeff: Overtone (\url{http://overtone.github.io})
\bibitem{Anti EP} Autechre: Anti EP (\url{https://en.wikipedia.org/wiki/Anti_EP})
